---
title: "Git example"
output: 
  github_document:
    html_preview: TRUE
---

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
```


# Introduction

Just a sentence to check that git works from my virtual PC.
I think it`s fixed now. Merge conflict opens in RStudio editor also on PC.

## Density plot

```{r xdensity}
set.seed(5566)
x <- data.frame(x=rnorm(1000000, mean = 2, sd = 1))
mean(x$x); sd(x$x)
ggplot(x, aes(x)) +
  geom_density()
rm(x)
```

## Points plot

We will be using the `cars` dataset. See `help(cars)` for details about the two variables.

```{r cars-summary}
summary(cars)
```

```{r cars-points-plot}
ggplot(cars, mapping = aes(x = speed, y = dist)) +
  geom_point()
```

### Spline

We might want to add a smooth.

```{r cars-points-plot-smooth, message=FALSE}
ggplot(cars, mapping = aes(x = speed, y = dist)) +
  geom_point() +
  geom_smooth()
```
Will this line be merged without ptoblem.

### Linear model

We might also want a plain linear model.

```{r cars-points-plot-smooth-lm, message=FALSE}
ggplot(cars, mapping = aes(x = speed, y = dist)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r summary-lm}
mod <- lm(dist ~ speed, data = cars)
summary(mod)
```

## Conclusions

We are now working in branch conclusions. The conclusion must be that git is a lot of fun, but can sometimes be a little bit challenging. Remember: Keep smiling ;-)

This just to add some text.
